\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-19 doc/acknowledgments.tex
Switched to MIT license #125
Fixed all missing references, merged bib files back into one. Also added CFHTLS acknowledgment text and website URL footnote. Closes #130

We thank all \Ncollaboration members of the \sw community for their
contributions to the project so far. A complete list of collaborators is
given at \texttt{http://spacewarps.org/\#/results/CFHTLS}.

@@

>>>>

We thank all \Ncollaboration members of the \sw community for their
contributions to the project so far. A complete list of collaborators is
provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.

@@

The CFHTLS data used in this work are based on observations obtained with
MegaPrime/MegaCam, a joint project of CFHT and CEA/IRFU, at the
Canada-France-Hawaii Telescope (CFHT) which is operated by the National Research
Council (NRC) of Canada, the Institut National des Science de l'Univers of the
Centre National de la Recherche Scientifique (CNRS) of France, and the
University of Hawaii. This work is based in part on data products produced at
Terapix available at the Canadian Astronomy Data Centre as part of the
Canada-France-Hawaii Telescope Legacy Survey, a collaborative project of NRC and
CNRS.

### 2015-04-19 doc/sw-cfhtls.tex
Fixed all missing references, merged bib files back into one. Also added CFHTLS acknowledgment text and website URL footnote. Closes #130

%%% ENSURE WORD LIMIT IS 250
We report the discovery of 28 promising and a total of 58 new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lenses missed by lens finding robots (the \rf on galaxy scales
and \af on group/cluster scales), which have been previously used to
mine the \cfhtls for lenses.  We compare some properties of lens samples
detected by these algorithms to the \sw sample and found that they are
broadly similar.  The image separation distribution calculated from the
\sw discovered sample shows that our previous constraints on the average
density profile of the lens population are robust. \sw recovers about
60\% of the known sample and the new candidates show a richer variety
compared to the lenses found by the two robots. We find that analyzing
only those classifications which are performed by the high power
volunteers, \sw can achieve a detection rate of up to 75\% of the known
lens sample.  Training and calibration of the performance of citizen
scientists is crucial for the success of \sw. We also present the SIMCT
pipeline, used for generating a sample of realistic simulated lensed
images in the CFHTLS, and a sample of duds and false positives used in
the training.  Such a training sample has a legacy value for testing
future lens finding algorithms. We make our training sample publicly
available.
%%% ENSURE WORD LIMIT IS 250

@@

In this paper (Paper II hereafter), we describe our first lens search
using data from the Canada-France-Hawaii Telescope Legacy Survey
(\cfhtls). This paper is organised as follows. In
\Sref{sec:data}, we introduce the \cfhtls imaging data and the
previously published lens samples from the \cfhtls. We generated a training sample, 
consisting of simulated lenses, duds and false positives, in order to
aid the \sw volunteers in the process of finding lenses. We give details of this
training sample in \Sref{sec:ts} and \Sref{sec:dfp}. In \Sref{sec:swap},
we briefly describe how the classifications of images from the volunteers are
turned into a catalog of plausible candidates (for further details, see
Paper I). In \Sref{sec:results}, we present the new lens candidates from \sw and
compare it to the lens samples produced by a few robotic searches from
the \cfhtls in the past. Next, we discuss what kind of lenses are detected
or missed by the algorithms and \sw in \Sref{sec:discuss}. The summary
and conclusions are given in \Sref{sec:conclude}.

@@

\bibliographystyle{apj}
%\bibliography{references}
\bibliography{references_cfhtls}

>>>>

%%% ENSURE WORD LIMIT IS 250
We report the discovery of 28 promising and a total of 58 new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lenses missed by lens finding robots (the \rf on galaxy scales
and \af on group/cluster scales), which have been previously used to
mine the \cfhtls for lenses.  We compare some properties of lens samples
detected by these algorithms to the \sw sample and found that they are
broadly similar.  The image separation distribution calculated from the
\sw discovered sample shows that our previous constraints on the average
density profile of the lens population are robust. \sw recovers about
60\% of the known sample and the new candidates show a richer variety
compared to the lenses found by the two robots. We find that analyzing
only those classifications which are performed by the high power
volunteers, \sw can achieve a detection rate of up to 75\% of the known
lens sample.  Training and calibration of the performance of citizen
scientists is crucial for the success of \sw. We also present the SIMCT
pipeline, used for generating a sample of realistic simulated lensed
images in the \cfhtls, and a sample of duds and false positives used in
the training.  Such a training sample has a legacy value for testing
future lens finding algorithms. We make our training sample publicly
available.
%%% ENSURE WORD LIMIT IS 250

@@

In this paper (Paper II hereafter), we describe our first lens search
using data from the Canada-France-Hawaii Telescope Legacy Survey
(\cfhtls\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}).
This paper is organised as follows. In
\Sref{sec:data}, we introduce the \cfhtls imaging data and the
previously published lens samples from the \cfhtls. We generated a training sample,
consisting of simulated lenses, duds and false positives, in order to
aid the \sw volunteers in the process of finding lenses. We give details of this
training sample in \Sref{sec:ts} and \Sref{sec:dfp}. In \Sref{sec:swap},
we briefly describe how the classifications of images from the volunteers are
turned into a catalog of plausible candidates (for further details, see
Paper I). In \Sref{sec:results}, we present the new lens candidates from \sw and
compare it to the lens samples produced by a few robotic searches from
the \cfhtls in the past. Next, we discuss what kind of lenses are detected
or missed by the algorithms and \sw in \Sref{sec:discuss}. The summary
and conclusions are given in \Sref{sec:conclude}.

@@

\bibliographystyle{apj}
\bibliography{references}
